---
title: "reading_files_overlays"
output: html_document
---

## Reading files 

In this part I am going to read files. Files are BlackMtnLRect, BM, BM_modified_TC_FireHist. 

```{r}
library(sf)
library(sp)
library(tidyverse)
library(raster)
library(rasterVis)
library(reshape2)
library(akima)
library(RColorBrewer)
library(viridis)
library(scales)
library(animation)
library(png)
```


```{r}
blc_mnt <- raster('../Data/BlackMtnLRect.tif')
bm <- raster('../Data/BM.tif')
bm_firhist <- read_sf('../Data/BM_modified_TC_FireHist.shp')


bm_firhist %>% 
  filter(Type == "PB") %>% 
  filter(YEARNUM <2013 & YEARNUM > 2005)


levelplot(blc_mnt, par.settings = BTCTheme )+ 
  levelplot(bm,par.settings = GrTheme) 
  

plot3D(bm)





ggplot()+
geom_sf(data = bm_firhist,aes(fill = IGNITION))+
  geom_sf_text(data = bm_firhist, aes(label = OBJECTID))




```



```{r}

levelplot(bm,par.settings = GrTheme)

```





```{r}



st_crs(bm_firhist)
r <- "+proj=utm +zone=55 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
crs(bm,asText =T )


## change the crs.
prj_rstr_dem  <- projectRaster(bm,crs = r,method='bilinear')


t <- crs(bm) 

```



```{r}



crp_172 <- crop(prj_rstr_dem,extent(bm_firhist %>% 
  filter(OBJECTID == 172)))


plot3D(crp_172)

z_172 <- raster::extract(prj_rstr_dem,bm_firhist %>% 
  filter(OBJECTID == 172),method = "bilinear",df = T,cellnumbers = T)

ints_172 <- raster::intersect(prj_rstr_dem, bm_firhist %>% filter(OBJECTID == 172))

plot3D(ints_172)

bm_firhist %>% 
  filter(OBJECTID == 172) %>% 
  st_coordinates()

str(ints_172)
str(z_172)

xy_172 <- coordinates(prj_rstr_dem)[z_172$cell,]

s_172 <- cbind(data.frame(xy_172),z =z_172$BM)

rgl::plot3d(s_172$x,s_172$y,s_172$z)


ipl172 <- interp(s_172$x,s_172$y,s_172$z)


colZ <- brewer.pal(9,"OrRd")
rgl::surface3d(ipl172$x,ipl172$y,ipl172$z,color = colZ,alpha=0.75)


```





```{r}

     x <- sampleRegular(prj_rstr_dem, size=1e5, asRaster=TRUE)
                  X <- xFromCol(x,1:ncol(x))
                  Y <- yFromRow(x, nrow(x):1)
                  Z <- t((getValues(x, format='matrix'))[nrow(x):1,])
                  
                  background <- min(Z, na.rm=TRUE) - 1
                  Z[is.na(Z)] <- background
                  
                  zlim <- range(Z)
                  zlen <- zlim[2] - zlim[1] + 1
                  xlen <- max(X) - min(X)
                  ylen <- max(Y) - min(Y)
                  at = 8
                  at <- do.breaks(zlim, at)
                  col <- viridis_pal(option = "magma",direction = -1)(length(at))
                  zcolor <- level.colors(Z, at=at, col.regions= col)
                  rgl::open3d()
                  rgl::rgl.surface(X, Y, Z, color=zcolor, alpha=0.5,back = "lines")
                  at = 8
                  at <- do.breaks(range(s_172$z), at)
                  col <- viridis_pal(option = "cividis")(length(at))
                  colZ <- level.colors(s_172$z, at=at, col.regions= col)
                  rgl::rgl.surface(ipl172$x,ipl172$y,ipl172$z+100,color = colZ,alpha = 1,back = "lines")
            
                  
## if I want to overlay a surface over another surface I should make sure that they have same x and Y limit.  
## for(x in all.sub) X[rownames(x),colnames(x)] <- x
```




instead of drawing the whole fire what if I plot the primeter of the fires.
```{r}
####
crds_172 <- st_coordinates(st_boundary(bm_firhist %>% 
  filter(OBJECTID == 172)))[,c(1,2)]

#### extracting z dimension for boundary points of the fire.

lne_z <- function(X,Y,...){
  tmp_pnt <- SpatialPoints(cbind(x = X,y = Y),
                    proj4string = CRS("+proj=utm +zone=55 +south +ellps=GRS80 +units=m +no_defs"))
  ans <- raster::extract(prj_rstr_dem,tmp_pnt)
  ans
}

prmt_172 <- cbind( x = crds_172[,1],y = crds_172[,2],z = as_tibble(crds_172) %>% 
   pmap_dbl(lne_z))
     

x <- sampleRegular(prj_rstr_dem, size=1e5, asRaster=TRUE)
                  X <- xFromCol(x,1:ncol(x))
                  Y <- yFromRow(x, nrow(x):1)
                  Z <- t((getValues(x, format='matrix'))[nrow(x):1,])
                  
                  background <- min(Z, na.rm=TRUE) - 1
                  Z[is.na(Z)] <- background
                  
                  zlim <- range(Z)
                  zlen <- zlim[2] - zlim[1] + 1
                  xlen <- max(X) - min(X)
                  ylen <- max(Y) - min(Y)
                  at = 8
                  at <- do.breaks(zlim, at)
                  col <- viridis_pal(option = "magma",direction = -1)(length(at))
                  zcolor <- level.colors(Z, at=at, col.regions= col)
                  rgl::open3d()
                  rgl::lines3d(prmt_172[,1],prmt_172[,2],prmt_172[,3] ,color = "red",lwd = 5,smooth = T)
                  rgl::surface3d(X, Y, Z, color=zcolor, alpha=0.8,back = "filled")
                  rgl::aspect3d(1, 1, 0.2)

```



This function provides a way to visualise the boundary of a fire polygon over a DEM raster. To come up with the first protoype. I faced a problem with coordinate reference system of DEM raster. The problem was finding the right CRS for DEM. The crs is the specific for satelite image provided by google map.



```{r}

### This function takes a DEM raster and a shape file. 
### The function assumes that DEM raster and fire shape file overlay. 
### Maybe this is something that function should check before running.
### at the moment only one fire preimeter can be displayed
### the possiblity of plotting more fire will be investigated.
### add a test to see if selected shapefile intersect with the DEM raster



lne_z <- function(ln,lt,dem,dem_crs,...){
  tmp_pnt <- SpatialPoints(cbind(x = ln ,y = lt ),
                    proj4string = CRS(dem_crs))
  ans <- raster::extract(dem,tmp_pnt)
  ans
}

## prem is the shapefile that will be used to extract its boundary

prem_over_dem <- function(dem, prem,flat.ratio = 0.3){
  
if( !is.na(st_crs(prem)) & !is.na(crs(dem))){  

dem_crs <- crs(dem,asText = T) 
## change the crs.
st_transform(prem,crs = dem_crs)

#### coordinates of boundaries
crds_bnd  <- st_coordinates(st_boundary(prem))[,c(1,2)]


#### extracting z dimension for boundary points of the fire.
prmt_hght <- cbind( x = crds_bnd[,1],y = crds_bnd[,2],z = as_tibble(crds_bnd) %>% 
   pmap_dbl(~lne_z(ln = .x ,lt= .y,dem = dem ,dem_crs = )))
     

x <- sampleRegular(dem, size=1e5, asRaster=TRUE)
                  X <- xFromCol(x,1:ncol(x))
                  Y <- yFromRow(x, nrow(x):1)
                  Z <- t((getValues(x, format='matrix'))[nrow(x):1,])
                  
                  background <- min(Z, na.rm=TRUE) - 1
                  Z[is.na(Z)] <- background
                  
                  zlim <- range(Z)
                  zlen <- zlim[2] - zlim[1] + 1
                  xlen <- max(X) - min(X)
                  ylen <- max(Y) - min(Y)
                  at = 8
                  at <- do.breaks(zlim, at)
                  col <- viridis_pal(option = "viridis",direction = -1)(length(at))
                  zcolor <- level.colors(Z, at=at, col.regions= col)
                  rgl::open3d()
                  rgl::lines3d(prmt_hght[,1],prmt_hght[,2],prmt_hght[,3] ,color = "red",lwd = 5,smooth = T)
                  rgl::surface3d(X, Y, Z, color=zcolor, alpha=1,back = "filled")
                  rgl::aspect3d(1, 1, flat.ratio)
                  
                  print(prmt_hght)
  }
}





prem_over_dem(bm,bm_firhist %>% 
  filter(OBJECTID == 172),flat.ratio = 0.25) 
rgl::rgl.viewpoint(20, -50)

## printing snapshots of rgl plots as png files.
# for (i in 1:45) {
#   rgl::rgl.viewpoint(20, -50+i)
#   filename <- paste("pic", formatC(i, digits = 1, flag = "0"), ".png", sep = "")
#   rgl::rgl.snapshot(filename)
# }


ggplot()+
geom_sf(data = bm_firhist %>% 
  filter(OBJECTID == 11),aes(fill = IGNITION))

raster::intersect(prj_rstr_dem, bm_firhist %>% filter(OBJECTID == 15))

```

```{r}



rgl::shade3d(rgl::oh3d(), color = "red")
rgl::rgl.bringtotop()
rgl::rgl.viewpoint(0, 20)




# library(animation)
# ## make sure ImageMagick has been installed in your system
# saveGIF({
#   for (i in 1:10) plot(runif(10), ylim = 0:1)
# })
```
 This function outputs a raster based on some criteria.
 
```{r}




bm_firhist %>% 
  filter(Type == "PB") %>% 
  filter(YEARNUM <2013 & YEARNUM > 2005) 







r <- raster::raster(nrows = 10,ncols = 10,crs = "+proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m +nadgrids=@null +no_defs")


rgdal::projInfo(type = "units")


# hist_rast <- function(shpfile = NULL, cellSize = 25, snapRaster = NULL,oldestfire = NULL){
#   
#   
# }
```
 
 
